---
title: "Ordination"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ordination}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r options, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library("abmiscr")
suppressMessages(library("vegan"))
data("varespec")
ggplot2::theme_set(ggplot2::theme_classic(base_size = 10))
```

One common use case is the ability to run and compare a number of ordinations, particularly their stress. I use the `vegan::varespec` dataset for an example.

First, I calculate a series of NMDS ordinations using a simple helper function `calc_mds()`. Oftentimes, keeping the intermediate distance matrix and list of NMDS ordinations is helpful, so I assign those to separate objects:

```{r mds-info}
dist_matrix <- calc_dist_matrix(varespec)
mds_list <- get_mds_list(dist_matrix)
mds_info <- get_mds_info(mds_list)
mds_info
```

Then, as a visual, I create a plot that compares the stress versus the number of dimensions:

```{r stress-vs-dim-plot, fig.width = 4}
plot_stress_dim(mds_info)
```
